A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-28 manuscript.Rmd
added figure ref

<!-- could andreas write this? --->
We identified the following common threat to reproducibility: <!-- CJ How did you identify these causes? Is this exhaustive?-->

@@

To summarize, the workflow by @Peikert2019 requires four components, dynamic document generation (using R Markdown), version control (using Git), internal dependency management (using Make), containerization (using Docker). While R Markdown and git are well integrated into the R environment through R Studio, Make and Docker require a level of expertise that is often beyond the training of scholars outside studies of information technology, which represents a considerable hurdle in the acceptance and implementation of the workflow. To remove this hurdle, we have developed a new R package `repro` that supports scholars in setting up, maintaining, and reproducing research projects in R. In the remainder, we will walk you through a complete research project, from sketching the very first idea over preregistration, data analysis, and submission of a preprint while focusing on how the `repro`-package enables users to maintain reproducibility of all steps.

<!-- TODO Andreas: Internal and externdal dependencies -->

>>>>

We identified the following common threat to reproducibility: <!-- CJ How did you identify these causes? Is this exhaustive?-->

@@

To summarize, the workflow by @Peikert2019 requires four components (see Figure \@ref{schematic}), dynamic document generation (using R Markdown), version control (using Git), internal dependency management (using Make), containerization (using Docker). While R Markdown and git are well integrated into the R environment through R Studio, Make and Docker require a level of expertise that is often beyond the training of scholars outside studies of information technology, which represents a considerable hurdle in the acceptance and implementation of the workflow. To remove this hurdle, we have developed a new R package `repro` that supports scholars in setting up, maintaining, and reproducing research projects in R. In the remainder, we will walk you through a complete research project, from sketching the very first idea over preregistration, data analysis, and submission of a preprint while focusing on how the `repro`-package enables users to maintain reproducibility of all steps.
